---
title: "spaceMovie color palette generator"
author: "Chris Hamm"
date: "`r format(Sys.Date())`"
output:  
      html_document:  
        keep_md: TRUE 
---
```{r, echo = FALSE}
knitr::opts_chunk$set(
echo = TRUE, 
fig.align = "center",
fig.path = "figure/"
)
```

## Space Movie color palettes
The colors used in this package were all found using publically available sources, many of them from LucasArts themselves. For example:

- [Rebels](http://www.starwars.com/news/star-wars-rebels-costume-color-guide-for-padawans-twileks-and-more)
- [Imperials](http://www.starwars.com/news/star-wars-rebels-costume-color-guide-for-imperials)

Kartik Ram's [Wes Anderson](https://github.com/karthik/wesanderson) color palette inspired me to create this package and I followed his implementation for consistency.


### Installation
```{r install, eval = FALSE}
devtools::install_github("butterflyology/spaceMovie")
```

### Usage
```{r usage}
library("spaceMovie")
```

### Chopper
```{r chopper}
library("ggplot2")
ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) +
  theme_bw() +
  geom_point(size = 3) +
  scale_color_manual(values = SW_palette("Chopper"))
```

### Boba
```{r Boba, fig.height = 1}
SW_palette("Boba")
```

### Zeb
```{r Zeb, fig.height = 1}
SW_palette("Zeb")
```

### Sabine
```{r Sabine, fig.height = 1}
SW_palette("Sabine")
```


### Main
```{r Main}
qplot(factor(cyl), data = mtcars, geom = "bar", fill=factor(vs)) +
  scale_fill_manual(values = SW_palette("Main"))
```

### Inquisitor volcano
```{r Inquisitor}
SW_colors_1 <- SW_palette("Inquisitor", 21, type = "continuous")
image(volcano, col = SW_colors_1, las = 1)
```

### Heat map
```{r Heat}
SW_colors_2 <- SW_palette("Hera", 100, type = "continuous")

ggplot(heatmap, aes(x = X2, y = X1, fill = value)) + 
  geom_tile() + 
  scale_fill_gradientn(colours = SW_colors_2) + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) + 
  coord_equal() 
```
