---
title: "*spaceMovie* basics"
author: "Chris Hamm"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{spaceMovie-basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  \usepackage[utf8]{inputenc}
---
```{r load, echo = FALSE}
library("spaceMovie")
```

This is a vignette to demonstrate the basics of using the *spaceMovie* package to generate color palettes.

The most basic form requires only that you call the function `SW_palette()` and provide one of the palette names. By default, all colors from that palette will be displayed.

### 'A New Hope'
```{r ANH, fig.height = 1}
SW_palette("TESB")
```

### Zeb from *Rebels*
```{r Zeb, fig.height = 1}
SW_palette("Zeb")
```

You may explicitly state the number of colors you would like.

### Sabine from *Rebels*
```{r Sabine, fig.height = 1}
SW_palette("Sabine", n = 3)
```


You can use *spaceMovie* to color code your plots, as with this example using `ggplot2`:

### Chopper
```{r chopper, fig.width = 5}
library("ggplot2")
ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) +
  theme_bw() +
  geom_point(size = 3) +
  scale_color_manual(values = SW_palette("Chopper")) +
  labs(y = "Sepal width", x = "Sepal length") +
  theme(legend.text = element_text(face = "italic"))
```

Here is a similar plot using base `R`:
```{r chopper-base, fig.width = 5, fig.height = 4}
plot(x = iris$Sepal.Length, y = iris$Sepal.Width, pch = 19, col = SW_palette("Chopper")[factor(iris$Species)], cex = 1.25, xlab = "Sepal length", ylab = "Sepal width", las = 1, ylim = c(2, 4.5), xlim = c(4, 8))
legend("topleft", col = SW_palette("Chopper"), pch = 19, bty = "n", legend = c(expression(paste(italic("setosa"))), c(expression(paste(italic("versicolor")))), c(expression(paste(italic("virginica"))))))
```


The `SW_palette` function also allows you to select `type = "continuous"`, which will fill in `n` number of colors.

### Boba
```{r Boba, fig.height = 1}
SW_palette("Boba", n = 21, type = "continuous")
```

Saving continuous palettes to an object may clean up your code a bit:

### A Boba Fett volcano!
```{r Boba_volcano, fig.width = 5, fig.height = 4}
SW_colors_1 <- SW_palette("Boba", 21, type = "continuous")
image(volcano, col = SW_colors_1, las = 1)
```



### Heat map
```{r Heat, fig.width = 5}
SW_colors_2 <- SW_palette("Hera", 100, type = "continuous")

ggplot(heatmap, aes(x = X2, y = X1, fill = value)) + 
  geom_tile() + 
  scale_fill_gradientn(colours = SW_colors_2) + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) + 
  coord_equal() 
```






